Dependent Object Types

### 2012-08-06 article.tex
case msel, not so convincing

\Case \textsc{sel}: $\Gamma \ts t_1.l_i : T$ knowing $\Gamma \ts t_1 :
T_1$, $\Gamma \ts T_1 \expand_z \seq{D}$, $l_i : V_i \in \seq{D}$ and
knowing either that $t_1 = p_1 \andl T = \subst p z {V_i}$ or that $z
\not\in \fn(V_i) \andl T = V_i$.

Need to show $t_1.l_i \in \rele k \Gamma - T$. Suppose $k > 0$ and $s
\in \rels k \Gamma -$. Suppose $\reductionl {t_1.l_i} s {t'} {s'}
\andl \irred {t'} {s'} \andl \Gamma' \in \relg \Gamma k {s'}
\Gamma$. Remains to show ${t'} \in \relv {k-j-1} {\Gamma'} {s'} T$.

By operational semantics, $\reductionl {t_1} s {t_1'} {s'} {j-1}$ and
$\irred {t_1'} {s'}$. By induction hypothesis, ${t_1'} \in \relv
{k-j+1-1} {\Gamma'} {s'} {T_1}$.

@@

\Case \textsc{msel}: \todo{case}.

>>>>

\Case \textsc{sel}: $\Gamma \ts t_1.l_i : T$ knowing $\Gamma \ts t_1 :
T_1$, $\Gamma \ts T_1 \expand_z \seq{D}$, $\ldecl {l_i} {V_i} \in
\seq{D}$ and knowing either that $t_1 = p_1 \andl T = \subst p z
    {V_i}$ or that $z \not\in \fn(V_i) \andl T = V_i$.

Need to show $t_1.l_i \in \rele k \Gamma - T$. Suppose $k > 0$ and $s
\in \rels k \Gamma -$. Suppose, for some $j \leq k$, $\reductionl
    {t_1.l_i} s {t'} {s'} j \andl \irred {t'} {s'} \andl \Gamma' \in
    \relg \Gamma k {s'} \Gamma$. Remains to show ${t'} \in \relv
          {k-j-1} {\Gamma'} {s'} T$.

By operational semantics and induction hypothesis, $\reductionl {t_1}
s {t_1'} {s'} {j-1}$ and $\irred {t_1'} {s'}$ and ${t_1'} \in \relv
{k-j+1-1} {\Gamma'} {s'} {T_1}$.

@@

\Case \textsc{msel}: $\Gamma \ts t_1.m_i(t_2) : T$ knowing $\Gamma \ts
t_1 : T_1$, $\Gamma \ts t_2 : T_2$, $\Gamma \ts T_1 \expand_z
\seq{D}$, $\mdecl {m_i} {S_i} {U_i} \in \seq{D}$ and knowing either
that $t_1 = p_1 \andl S = \subst p z {S_i} \andl T = \subst p z {U_i}$
or that $z \not\in \fn(S_i) \andl z \not\in \fn(U_i) \andl S = S_i \andl
T = U_i$.

Need to show $t_1.m_i(t_2) \in \rele k \Gamma - T$. Suppose $k > 0$
and $s \in \rels k \Gamma -$. Suppose, for some $j \leq k$,
$\reductionl {t_1.m_i(t_2)} s {t'} {s'} j \andl \irred {t'} {s'} \andl
\Gamma' \in \relg \Gamma k {s'} \Gamma$. Remains to show ${t'} \in
\relv {k-j-1} {\Gamma'} {s'} T$.

By operational semantics and induction hypotheses, $\reductionl {t_1}
s {t_1'} {s_1} {j_1}$ and $\irred {t_1'} {s_1}$ and $\reductionl {t_2}
{s_1} {t_2'} {s_2} {j_2}$ and $\irred {t_2'} {s_2}$ and ${t_1'} \in \relv
{k-j_1-1} {\Gamma_1} {s_1} {T_1}$ and ${t_2'} \in \relv {k-j_1-j_2-1}
{\Gamma_2} {s_2} {T_2}$.

By operational semantics, $\reductionl {t_1'.m_i(t_2')} {s_2} {\subst
  {t_2'} x_i t_i} {s_2} 1$. By substitution lemma, ${\subst {t_2'} x_i
  t_i} \in \rele {k-j_1-j_2-1} {\Gamma_2} {s_2} T$. So, $\reductionl
{\subst {t_2'} x_i t_i} {s_2} {t'} {s'} {j_3}$, with $j_1 + j_2 + j_3 +
1 = j$ implies what remains to be shown.
